Comprehensive Quality Awareness Automated Semantic Web Service Composition

### 2017-03-26 paper.tex
update

 \item To propose a PSO-based service composition approach that utilises the proposed comprehensive quality model. To do that we optimise a queue of web services by evaluating its decoded representations. These representations are the solutions for semantic web service composition.

@@

Semantic web service composition \cite{boustil2014semantic,bansal2016generalized,mier2015integrated} captures the semantic description of web services' parameters using some kind of logic (e.g., description logic) that ensuring the interoperability of web services, where the number of web services or length of a graph representation for web service composition is minimised to reach the optimised composition solutions. However, this evaluation approach does not guarantee optimised QoS of composition solutions.

QoS-aware web service composition is studied using traditional approaches or Evolutionary Computation (EC) techniques for finding near-optimised solutions. Qi et al. \cite{qi2010combining} propose a heuristic service composition method, named LOEM (Local Optimisation and Enumeration Method), where a small number of promising candidates related to each task are considered by local selection, and composition solutions are enumerated to reach the near-to-optimal QoS. However, there exists a scalability problem for the enumeration technique. EC techniques are used to automatically generate solutions with optimal QoS, which is considered to a NP-hard problem. Gupta et al. \cite{gupta2015optimization} employ a modified Genetic Algorithm (GA) using a binary string as an individual, which demands to be decoded into composition solutions. Genetic Programming (GP) are used by \cite{yu2013adaptive} to find optimal solutions, which is reached by penalising infeasible solutions using a fitness function. A hybrid approach employs both greedy search algorithm and GP is introduced in \cite{ma2015hybrid} to generate solutions that are functionally correct. In particularly, greedy search techniques have been used to generate directed acyclic graphs (DAGs) as composition solutions that is further transferred to tree structures for initialisation and mutation. To eliminating the transformation process from DAGs, a promising GraphEvol is proposed in \cite{da2015graphevol}, where web service composition are in a form of DAGs employing Graph-based evolutionary operators like crossover and mutation. An indirect PSO-based approach was introduced in \cite{da2016particle}. An optimised queue is used as an indirect representation that is decoded into a DAG-based solution. These QoS-aware approaches \cite{gupta2015optimization,qi2010combining,ma2015hybrid,da2016particle,da2015graphevol,yu2013adaptive} do not consider semantic matchmaking quality, which could lead to too specific outputs produced by the selected services, and this finding is supported by our first comparison experiment.

Only a few works \cite{fanjiang2014semantic,lecue2009optimizing,pop2009immune} consider both semantic matchmaking quality and QoS simultaneously. Lecue et al. \cite{lecue2009optimizing} propose a semi-automated web service composition using GA to encode a given abstract service workflow, where the semantic matchmaking quality is measured through evaluating the quality of semantic links that require a formal definition of ontology in Description Logic. This evaluation model takes huge cost and time for the domain experts to establish required ontology. Another GA-based approach \cite{fanjiang2014semantic} utilise process description language to encode pre-stored cases-based workflows, where workable services are composed to complete this workflow. The work \cite{pop2009immune} is an automated immune-inspired web service composition approach, where an indirect representation that a binary alphabet is used to encode a planning graph. However, this composition method is only evaluated on a set of scenarios.

In summary, despite a large number of approaches for semantic web service composition and QoS-aware service composition approaches, there is a lack of a fully automated semantic web service composition approach to optimise semantic matchmaking quality and QoS simultaneously. Therefore, we first propose a general comprehensive quality model that aims to achieve a better semantic matchmaking quality with a slight trade-off in QoS, and then we propose an automated PSO-based approach with explicit support for the comprehensive model to find optimal service compositions.

@@

The aim of web service composition considered in this paper is to automatically compose optimal solutions in considering both QoS and semantic matchmaking quality based on a user's request. The request is to provide inputs and obtain outputs. The resulting composition of this request is a composition solution with an optimal comprehensive quality in terms of semantic matchmaking quality and QoS. A motivating example of this problem is shown in Fig \ref{motivation}. The figure shows a DAG that represents a solution with four web services involved for a request $R$ as a composition task, where inputs of the task are \{TravelDepartureDate, HomeCity, ConferenceCity, TravelReturnDate \} and outputs are \{BusTicket, FlightTicket, TouristMap, HotelReservation \}. This is a classic example of travel planning problem for people who seek for booking services of airplanes, buses and hotels reservation, and also generating tourist maps for the conference city. The graph also contains edges that marked with connected outputs and inputs of two connected atomic services, which represent valid semantic matches that the outputs of a web service can be passed as the inputs of its successors.

@@

Although obtaining a correct combination of web service is essential, there are many ways to connect multiple web services chosen from a service repository. These web services provide different QoS in terms of availability, price, reliability and response time. Moreover, valid semantic matches between two connected web services could also have different matchmaking quality. For example, $Generate Map$ service produce $StreetMap$ which is considered to be a valid semantic match to $TouristMap$, while $Bus Service$ produce $BusTicket$ which is considered to be a better valid semantic match to $BusTicket$. The descriptions of these matched resources are captured in a taxonomy depicted in Fig .\ref{taxonomy}, where all the inputs and the outputs related to the web services are described for a travel planning problem. For example, the concept $Map$ and its sub-concept $urbanMap$ are assigned with a $touristMap$ instance and $streetMap$ instance respectively in Fig .\ref{taxonomy}. The valid semantic match is considered that an instance of $urban Map$ can be an instance of $Map$, but not vice versa. To demonstrate the motivation of proposing a comprehensive quality, we give a simple example. The service $GenerateMap$ with a output ($StreetMap$) and a price (``6.72") in the web service composition can be replace by a service $GenerateTouristMap$ with a different output ($TouristMap$) and a different price (``16.87") available in the service repository. This composition solution results in a better semantic matchmaking quality, but price negatively contributes to the QoS. Therefore, to reach the optimal solutions, we need to measure these changes to the solutions considering matchmaking quality and QoS simultaneously for automatically generated solutions.

\begin{figure}[h]
\centering
\fbox{\includegraphics[scale=.28]{taxonomy.pdf}}
 \caption{ A taxonomy of a travel planning domain}
 \label{taxonomy}
\end{figure}

@@

We herein give formal definitions of the concepts regarding the semantic web service composition problem utilised in our approach, and these concepts are captured in several models: a semantic web service model, a semantic matchmaking model, a weighted DAG composition model, and QoS calculation model, and composition problem model.

\textbf{Semantic Web Service Model}. The semantic web service model represents web services with functional descriptions, and how interoperability of web services enables matchmaking for automatically generating composition solutions.QoS-aware web service composition \cite{da2016particle,da2015graphevol,yu2013adaptive,ma2015hybrid}

@@

\textbf{Definition 2.} A semantic web service (hereafter "service") is defined as a tuple $S = \{ I_{S}, O_{S}, QoS_S \}$ $\in$ $\mathcal{SR}$, where $I_{S}$ is a set of service inputs that must be satisfied to invoke $S$, and $O_{S}$ is a set of service outputs returned by the execution of $S$. $I_{S}$ and $O_{S}$ are concept-related instances that are linked to the concepts $I^{C}_{S}$ and $O^{C}_{S}$, where $ I^{C}_{S}, O^{C}_{S}  \subseteq C$. $QoS_S = \{ t_s, c_s, r_s, a_s, ... \} $ is a set of non-functional attributes of $S$, it refers to response time $t_s$, cost $c_s$, reliability $r_s$, and availability $a_s$ \cite{zeng2003quality}. $\mathcal{SR}$ is a service repository consisting of a set of $S$.
\vspace{0.3cm}

@@

We use the returns of $type(a, b)$ to define a full matchmaking considered in the scenario of connecting two services through concept-related output and concept-related input.

@@

\textbf{QoS calculation Model in a DAG}
Four most often considered QoS parameters \cite{zeng2003quality} are response time, cost, reliability and availability described as follows:\textit{Response time} ($t_s$) measures the expected delay in seconds between the moment when a request is sent and the moment when the results are received.\textit{Cost} ($c_s$) is the amount of money that a service requester has to pay for executing the web service. \textit{Reliability} ($r_s$) is the probability that a request is correctly responded within the maximum expected time frame, which is expressed as a number between 1 and 0. \textit{Availability} ($a_s$) is the probability that a web service is accessible, which is expressed in the same way as $r_s$. The aggregation value of QoS in a DAG respect to the DAG's structures that determine how services associated with each other in a service composition. The QoS calculation models are described based on QoS aggregation method \cite{da2015graphevol} as follows:

$A$, $R$, $C$, $T$ is aggregated $a_s$, $r_s$, $c_s$ and $t_n$ respectively a given $WG$, where  $\{S_1, S_2, ... S_n\} \subset V$, such that: $A=\prod\limits^n_{k=1}a_k
$; $R=\prod\limits^n_{k=1}r_k$; $C=\sum\limits^n_{k=1}c_k$; $T$ is the time of most time-consumption path of $WG$, so $T = MAX \{timePath_n |n\in\{1,\ldots,m\}\}$.

@@

\textbf{Semantic matchmaking quality model}. Due to that the discretisational characteristics of different match types and values assigned to matching types driven by the cost of data manipulation \cite{lecue2009optimizing}, match types are considered to be one factor for the quality of matchmaking. For example, Exact matching type demands less time for computation compared to that of Plugin match. Another factor in concept similarity of two matched concepts. For example, two plugin types with different concept similarities: $publication \sqsubseteq printedmaterial$ and $romanticnovel \sqsubseteq printedmaterial$.

\textbf{Definition 5.} Given $full match(a \Rightarrow b)$, $q_{sim}(a, b)$ is a function that given a output-related concept of a service and a input-related concept of another service, it returns a concept similarity value between them.

The $q_{sim}(a, b)$ is calculated based on the edge counting method defined in the formula (\ref{equation1}) from \cite{shet2012new}, where $N_1$, $N_2$ and $N$ measure the distances from an output-related concept $a$, an input-related concept $b$, a closest common ancestor of these two matched $a$ and $b$ to the top concept of an ontology $O$ respectively. $\lambda$ is set to 0 if we do not measure the similarities of neighbourhood concepts, which is not the matching type considered in this paper.

@@

\textbf{Definition 5.} Given $full match(a \Rightarrow b)$, $sm(a,b)$ is a function that returns a pair of values consisitng of $type(a, b)$ and $q_{sim}(a, b)$ defined in Formula (\ref{equation2}).

@@

\textbf{Weighted DAG Composition Model}. web service composition is considered to be a data workflow, where services are chained together by their inputs and outputs using the two models defined before. Naturally, all these concepts can be captured in a weighted DAG as $WG = (V, E)$ , where:

@@

$E = \{e_{1}, e_{2},... e_{m} \}$ is a set of edges, where each edge has a set of incoming outputs $O_{S_{src}}$ from source service $S_{src}$ and a set of outgoing inputs $I_{S_{src}}$ from target service $S_{tar}$.

@@

Since each $e$ defined in $E$ could have more than one $fullmatch(a \Rightarrow b)$ form a edge $e$. Therefore, semantic matchmaking quality of one $e$, denoted as $sm_e$ is defined in formula (\ref{equation3}), where $type_{e}$ and $sim_{e}$ are the average values of all involved $type(a, b)$ and $q_{sim}(a, b)$ respectively.

@@

The semantic matchmaking quality $SM$ is futher aggregated with considering all $\{e_{1}, e_{2},... e_{m} \}$ in $E$, calculated by following the formula (\ref{eqSM})(\ref{equation6})(\ref{equation7}). Consequently, in Formula \ref{eqCQ}, the comprehensive quality $CQ$ consists of the aggregated semantic matchmaking quality $SM$ and the QoS calculation in DAG discussed before.

@@

\subsection{Objective Function}
In real life, given a unique and optimised solution is always easier for customers to pick up directly when many quality criteria involved into decision making, rather than provided a set of solutions. It is very practical to define a single fitness as a weighted sum of all the quality related components in Formula (\ref{equation8}). Note that weights can be adjusted according to users' preferences. The function value of 1 means the best comprehensive quality and 0 means the worst. For this purpose, $MT$, $S$, $A$, $R$, $T$, and $C$ must be normalised so that the function value falls within the range from 0 to 1 using Formula (\ref{equation9}) and (\ref{equation10}), where the maximum and minimum value of $A$, $R$, $T$, and $C$ are calculated by all web services related to the composition task. $MT$ and $S$ are using a bound from 0 to 1. Therefore, the composition task is try to find maximised value of objective function associated to the solutions.

@@

Our comprehensive quality evaluation model is considered to be more general. Semantic matchmaking types (Exact and Plugin) are considered for discovering desired web service in QoS-aware web service composition  \cite{ma2015hybrid,da2016particle,da2015graphevol}, but there are no measurements of matchmaking types and concept similarities. Consequently, weights for $MT$ and $S$ are considered to be 0 in our propopsed comprehensive evaluation model, it turns to a widely used QoS evaluation model in \cite{ma2015hybrid,da2016particle,da2015graphevol}.
\section{PSO-based Approach to Comprehensive Quality-Aware Automated Semantic Web Service Composition}\label{qswsc_approach}

@@

\subsection{PSO-based Approach to QoS-Aware Semantic Web Service Composition}

>>>>

 \item To propose a PSO-based service composition approach that utilises the proposed comprehensive quality model. To do that we optimise a queue of web services by evaluating the comprehensive quality of its decoded representations.

@@

Semantic web service composition \cite{bansal2016generalized,boustil2014semantic,mier2015integrated} captures the semantic description of web services' parameters using some kind of logic (e.g., description logic) that ensuring the interoperability of web services, where the number of web services or length of a graph representation for web service composition is minimised to reach the optimised composition solutions. However, this evaluation approach does not guarantee an optimised QoS of composition solutions.

QoS-aware web service composition is studied using traditional approaches or Evolutionary Computation (EC) techniques for finding near-optimised solutions. Qi et al. \cite{qi2010combining} propose a heuristic service composition method, named LOEM (Local Optimisation and Enumeration Method), where a small number of promising candidates related to each task are considered by local selection, and composition solutions are enumerated to reach the near-to-optimal QoS. However, there exists a scalability problem for the enumeration technique. EC techniques are used to automatically generate solutions with optimal QoS, which is considered to a NP-hard problem. Gupta et al. \cite{gupta2015optimization} employ a modified Genetic Algorithm (GA) using a binary string as an individual, which demands to be decoded into composition solutions. Genetic Programming (GP) are used by \cite{yu2013adaptive} to find optimal solutions, which is reached by penalising infeasible solutions using a fitness function. A hybrid approach employs both greedy search algorithm and GP introduced in \cite{ma2015hybrid} to generate solutions that are functionally correct. In particularly, greedy search techniques have been used to generate directed acyclic graphs (DAGs) as composition solutions that is further transferred to tree structures for initialisation and mutation. To eliminating the transformation process from DAGs, a promising GraphEvol is proposed in \cite{da2015graphevol}, where web service composition are in a form of DAGs employing Graph-based evolutionary operators like crossover and mutation. An indirect PSO-based approach was introduced in \cite{da2016particle}. An optimised queue is used as an indirect representation that is decoded into a DAG-based solution. These QoS-aware approaches \cite{gupta2015optimization,qi2010combining,ma2015hybrid,da2016particle,da2015graphevol,yu2013adaptive} do not consider semantic matchmaking quality, which could lead to too specific outputs produced by the selected services, and this finding is supported by our first comparison experiment.

Only a few works \cite{fanjiang2014semantic,lecue2009optimizing,pop2009immune} consider both semantic matchmaking quality and QoS simultaneously. Lecue et al. \cite{lecue2009optimizing} propose a semi-automated web service composition using GA to encode a given abstract service workflow, where the semantic matchmaking quality is measured through evaluating the quality of semantic links that require a complete and formal definition of ontology in Description Logic. This evaluation model takes huge cost and time for the domain experts to establish required ontology. Another GA-based approach \cite{fanjiang2014semantic} utilise process description language to encode pre-stored cases-based workflows, where workable services are composed to complete this workflow. The work \cite{pop2009immune} is an automated immune-inspired web service composition approach, where an indirect representation that a binary alphabet is used to encode a planning graph. However, this composition method is only evaluated on a set of scenarios.

In summary, despite a large number of approaches for semantic web service composition and QoS-aware service composition approaches, there is a lack of a fully automated semantic web service composition approach to optimise semantic matchmaking quality and QoS simultaneously, and this approach must be tested utilising benchmark dataset. Therefore, we first propose a general comprehensive quality model that aims to achieve a better semantic matchmaking quality with a slight trade-off in QoS, and then we propose an automated PSO-based approach with explicit support for the comprehensive model to find optimal service compositions.

@@

The aim of web service composition considered in this paper is to automatically compose optimal solutions in considering both QoS and semantic matchmaking quality based on a user's request. The request is to provide inputs and obtain outputs. The resulting composition of this request is a composition solution with an optimal comprehensive quality in terms of semantic matchmaking quality and QoS. A motivating example of this problem is shown in Fig \ref{motivation}. The figure shows a DAG that represents a solution with four web services involved for a request $R$ as a composition task, where inputs of the task are \{$TravelDepartureDate$, $HomeCity$, $ConferenceCity$, $TravelReturnDate$ \} and outputs are \{$BusTicket$, $FlightTicket$, $TouristMap$, $HotelReservation$ \}. This is a classic example of travel planning problem for people who seek for booking services of airplanes, buses and hotels reservation, and also generating tourist maps for the conference city. The graph also contains edges that marked with connected outputs and inputs of two connected atomic services, which represent valid semantic matches that the outputs of a web service can be passed as the inputs of its successors.

@@

Although obtaining a correct combination of web service is essential, there are many ways to connect multiple web services chosen from a service repository. These web services provide different QoS in terms of availability, price, reliability and response time. Moreover, valid semantic matches between two connected web services could also have different matchmaking quality. For example, $Generate Map$ service produce $StreetMap$ which is considered to be a valid semantic match to $TouristMap$, but $Bus Service$ produce $BusTicket$ which is considered to be a better valid semantic match to $BusTicket$. The descriptions of these matched resources are captured in a ontology depicted in Fig .\ref{taxonomy}, where all the inputs and the outputs related to the web services are described for the travel planning problem discuss here. For example, the concept $Map$ and its sub-concept $urbanMap$ are assigned with a $touristMap$ instance and $streetMap$ instance respectively in Fig .\ref{taxonomy}. The valid semantic match is considered that an instance of $urban Map$ can be an instance of $Map$, but not vice versa. To demonstrate the motivation of proposing a comprehensive quality, we give a simple example here. The service $GenerateMap$ with a output ($StreetMap$) and a price (``6.72") in the web service composition can be replace by a service $GenerateTouristMap$ with a different output ($TouristMap$) and a different price (``16.87") available in the service repository. This composition solution results in a better semantic matchmaking quality, but price negatively contributes to the QoS. Therefore, to reach the optimal solutions automatically, we need to measure these changes to the solutions considering matchmaking quality and QoS simultaneously.

\begin{figure}[h]
\centering
\fbox{\includegraphics[scale=.28]{taxonomy.pdf}}
 \caption{ An ontology of a travel planning domain}
 \label{taxonomy}
\end{figure}

@@

We herein give formal definitions of the concepts regarding the semantic web service composition problem utilised in our approach, and these concepts are captured in several models as follows.

\textbf{Semantic Web Service Model}. The semantic web service model represents web services with functional descriptions, and how interoperability of web services enables matchmaking for automatically generating composition solutions.

@@

\textbf{Definition 2.} A semantic web service (hereafter "service") is defined as a tuple $S = \{ I_{S}, O_{S}, QoS_S \}$ $\in$ $\mathcal{SR}$, where $I_{S}$ is a set of service inputs that must be satisfied to invoke $S$, and $O_{S}$ is a set of service outputs returned by the execution of $S$. $I_{S}$ and $O_{S}$ are concept-related instances that are linked to their corresponding concepts $I^{C}_{S}$ and $O^{C}_{S}$, where $ I^{C}_{S}, O^{C}_{S}  \subseteq C$. $QoS_S = \{ t_s, c_s, r_s, a_s, ... \} $ is a set of non-functional attributes of $S$, it refers to response time $t_s$, cost $c_s$, reliability $r_s$, and availability $a_s$ \cite{zeng2003quality}. $\mathcal{SR}$ is a service repository consisting of a set of $S$.
\vspace{0.3cm}

@@

We use $type(a, b)$ to define a full matchmaking considered in the scenario of connecting two services through concept-related output and concept-related input.

@@

\textbf{QoS calculation Model in a DAG}
Four most often considered QoS parameters \cite{zeng2003quality} are response time, cost, reliability and availability described as follows: \textit{Response time} ($t_s$) measures the expected delay in seconds between the moment when a request is sent and the moment when the results are received.\textit{Cost} ($c_s$) is the amount of money that a service requester has to pay for executing the web service. \textit{Reliability} ($r_s$) is the probability that a request is correctly responded within the maximum expected time frame, which is expressed as a number between 1 and 0. \textit{Availability} ($a_s$) is the probability that a web service is accessible, which is expressed in the same way as $r_s$. The aggregation value of QoS in a DAG respect to the DAG's structures that determine how services associated with each other in a service composition. The QoS calculation models are described based on QoS aggregation method \cite{da2015graphevol} as follows:

$A$, $R$, $C$, $T$ is aggregated $a_s$, $r_s$, $c_s$ and $t_n$ respectively with a given $WG$, where  $\{S_1, S_2, ... S_n\} \subset V$, such that: $A=\prod\limits^n_{k=1}a_k
$; $R=\prod\limits^n_{k=1}r_k$; $C=\sum\limits^n_{k=1}c_k$; $T$ is the time of most time-consumption path of $WG$, so $T = MAX \{timePath()_n |n\in\{1,\ldots,m\}\}$ where $m$ is the number of $WG$ path, and $timePath() = \sum\limits^j_{k=1}t_k$, where $j$ is the number of services involved this path.

@@

\textbf{Semantic matchmaking quality model}. Due to that the discretisational characteristics of different match types and values assigned to matching types driven by the cost of data manipulation \cite{lecue2009optimizing}, match types are considered to be one factor for the quality of matchmaking. For example, Exact matching type demands less time for computation compared to that of Plugin match. Another factor is concept similarity of two matched concepts. For example, two plugin types, $publication \sqsubseteq printedmaterial$ and $romanticnovel \sqsubseteq printedmaterial$, are associated with different similarities.

\textbf{Definition 5.} Given $full match(a \Rightarrow b)$, $q_{sim}(a, b)$ is a function that given a output-related concept $a$ of a service and a input-related concept $b$ of another service, it returns a concept similarity value between $a$ and $b$.

The $q_{sim}(a, b)$ is calculated based on the edge counting method defined in the formula (\ref{equation1}) from \cite{shet2012new}, where $N_1$, $N_2$ and $N$ measure the distances from an output-related concept $a$, an input-related concept $b$, a closest common ancestor of these two matched $a$ and $b$ to the top concept of an ontology $O$ respectively. $\lambda$ is set to 0 as we do not measure the similarities of neighbourhood concepts, which is not the matching type considered in this paper.

@@

\textbf{Definition 6.} Given $full match(a \Rightarrow b)$, $sm(a,b)$ is a function for measuring semantic matchmaking quality between two concepts, which returns a pair of values consisting of $type(a, b)$ and $q_{sim}(a, b)$ defined in Formula (\ref{equation2}).

@@

\textbf{Weighted DAG Composition Model}. web service composition is considered to be a data workflow, where services are chained together by their inputs and outputs using the two models defined before. All these concepts are captured and tackled in a weighted DAG as $WG = (V, E)$ , where:

@@

$E = \{e_{1}, e_{2},... e_{m} \}$ is a set of edges, where each edge has a set of incoming outputs $O_{S_{src}}$ from source service $S_{src}$ and a set of outgoing inputs $I_{S_{tar}}$ from target service $S_{tar}$.

@@

Since each $e$ defined in $E$ could have more than one $fullmatch(a \Rightarrow b)$ form a edge. Therefore, semantic matchmaking quality of one edge, denoted as $sm_e$ is defined in formula (\ref{equation3}), where $type_{e}$ and $sim_{e}$ are the average values of all involved $type(a, b)$ and $q_{sim}(a, b)$ respectively.

@@

The semantic matchmaking quality $SM$ is further aggregated with considering all $\{e_{1}, e_{2},... e_{m} \}$ in $E$, calculated by following the formula (\ref{eqSM})(\ref{equation6})(\ref{equation7}). Consequently, in Formula \ref{eqCQ}, the comprehensive quality $CQ$ consists of the aggregated semantic matchmaking quality $SM$ and the QoS calculation in DAG discussed before.

@@

\subsection{Objective Function}
In real life, given a unique and optimised solution is always easier for customers to pick up directly when many quality criteria involved into decision making, rather than provided a set of solutions. It is very practical to define a single fitness as a weighted sum of all the quality related components in Formula (\ref{equation8}). Note that weights can be adjusted according to users' preferences. The function value of 1 means the best comprehensive quality and 0 means the worst. For this purpose, $MT$, $S$, $A$, $R$, $T$, and $C$ must be normalised so that the function value falls within the range from 0 to 1 using Formula (\ref{equation9}) and (\ref{equation10}), where the maximum and minimum value of $A$, $R$, $T$, and $C$ are calculated by all web services candidates to the composition task, which are generated by a greedy search discussed in Sect.\ref{PSO_based_approach}. $MT$ and $S$ are using a bound from 0 to 1. Therefore, the composition task is try to find maximised value of objective function associated to the solutions.

@@

Our comprehensive quality evaluation model is considered to be more general. Two semantic matchmaking types (Exact and Plugin) are considered for discovering desired web service in recent QoS-aware web service composition  \cite{ma2015hybrid,da2016particle,da2015graphevol}, but there are no measurements of matchmaking types and concept similarities in their approaches. Consequently, weights for $MT$ and $S$ are considered to be 0 in our proposed comprehensive evaluation model, it turns to be a widely used QoS evaluation model in \cite{ma2015hybrid,da2016particle,da2015graphevol}.
\section{PSO-based Approach to Comprehensive Quality-Aware Automated Semantic Web Service Composition}\label{qswsc_approach}

@@

\subsection{PSO-based Approach to QoS-Aware Semantic Web Service Composition}\label{PSO_based_approach}
